### 2023-02-26 manuscript.Rmd
Parse evoked conditions after pipeline update

# Read by-participant ERP averages and channel locations
evokeds <- read_csv(here(output_dir, "ave.csv"))

@@

# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv"))

>>>>

# Read by-participant ERP averages and channel locations
evokeds <- read_csv(here(output_dir, "ave.csv")) %>%
  separate(label, into = c("phase", "condition"), sep = "/")

@@

# Read grand-averaged power
tfr_grand_ave <- read_csv(here(output_dir, "tfr_grand_ave.csv")) %>%
  separate(label, into = c("phase", "condition"), sep = "/")
